---
title: "Testing code"
author: "Courtney Chan"
date: "November 14, 2018"
output: github_document
---
#Testing code for the final project

##To accomplish:
-Looking through the datasets we have available
-What kind of analysis do we want to see
-Review the sample final projects

Some links to keep in mind:
https://www.cnn.com/election/2018/exit-polls/texas/senate
https://www.texastribune.org/2018/10/31/ut-tt-poll-texans-say-immigration-border-security-top-issues/


```{r packages}
library(tidyverse)
library(rvest)
library(httr)

```

##scraping election results from the web

###New York Times voting results by county

```{r scraping election results for texas from the web table method}

url = "https://www.nytimes.com/elections/results/texas-senate"
nytimes_data = read_html(url)

nytimes_data

```

```{r extracting tables from webiste}
nytimes_data %>% 
  html_nodes(css = "table")

```
This seems to have created two tables from the website data.

```{r making 1st web table into tibbles?}

table_overall = (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[1]] %>%
  html_table()

```

Made the first table that which we have final results for the state of texas.

```{r making 2nd web table into another tibble}

table_county =  (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[2]] %>%
  html_table() %>% 
  slice(1:(n() - 1))

```


Made the second table which has all of the 254 county level data for Texas!


## comparing these county level election results to highly searched voter election interests in google

```{r reading in dataset voter searches}

district_searches = read_csv(file =  "./data/Search_Data_US_Congressional_District_04Nov2018.csv")

```


```{r Tx subdata}

TX_searches = 
  district_searches %>% janitor::clean_names() %>% 
  filter(state == "TX")

```


##uploading county congressional district txt file

```{r 113th congressional district table}

congress_district = read.csv(file = "./data/congress_district2.csv")

```

## comparing these county level election results to search results by candidate

