---
title: "Testing code"
output: 
  html_document:
    theme: flatly
---
#Testing code for the final project

##To accomplish:
-Looking through the datasets we have available
-Need Google Trend data for search terms such as "Cruz" vs "Rourke" or "midterm election" to see if number of searches correlate with # votes for each candidate or # registered voters
-What kind of analysis do we want to see
-Review the sample final projects

Some links to keep in mind:
https://www.cnn.com/election/2018/exit-polls/texas/senate
https://www.texastribune.org/2018/10/31/ut-tt-poll-texans-say-immigration-border-security-top-issues/


```{r packages}
library(tidyverse)
library(rvest)
library(httr)
library(ggridges)
library(tigris)
library(leaflet)
library(dplyr)
library(purrr)


```

##scraping election results from the web

###New York Times voting results by county

```{r scraping election results for texas from the web table method}

url = "https://www.nytimes.com/elections/results/texas-senate"
nytimes_data = read_html(url, col_types = "ccdd")

nytimes_data

```

```{r extracting tables from website}
nytimes_data %>% 
  html_nodes(css = "table")

```
This seems to have created two tables from the website data.

```{r making 1st web table into tibbles?}

table_overall = (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[1]] %>%
  html_table()
```

## Tidying overall table for exploratory analysis

```{r}
#remove the commas in the numbers first
table_overall$Votes <- gsub(",","",table_overall$Votes)
table_overall$Pct. <- gsub("%","",table_overall$Pct.)

#convert votes and percent to numeric
table_overall = 
  table_overall %>% 
  mutate(Votes = as.numeric(Votes), Pct. = as.numeric(Pct.))
```

## Bar Plot of Votes per Candidate

```{r bar_plot}
bar_overall =
  table_overall %>% 
  mutate(Candidate = as.factor(Candidate)) %>% 
  mutate(Candidate = forcats::fct_reorder(Candidate, Votes)) %>% 
  ggplot(aes(x = Candidate, y = Votes, fill = Party)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Number of Votes per Candidate",
    x = "Candidate",
    y = "Number of Votes"
  ) +
  scale_x_discrete(labels = c("Cruz* Ted Cruz*" = "Ted Cruz", "O'Rourke Beto O'Rourke" = "Beto O'Rourke",
                              "Dikeman Neal Dikeman" = "Neal Dikeman"))
  
bar_overall
```

This plot illustrates how it was a close race between the top two candidates, O'Rourke and Cruz. As Dikeman had very few votes, we decided to omit Dikeman from further analyses.

Made the first table that which we have final results for the state of texas.

```{r making 2nd web table into another tibble}

table_county =  (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[2]] %>%
  html_table() %>% 
  slice(1:(n() - 1)) %>% 
  select(-Rpt.) %>% 
  janitor::clean_names()

```

## Tidying county table

```{r}
#remove the commas in the numbers first
table_county$cruz <- gsub(",","",table_county$cruz)
table_county$o_rourke <- gsub(",","",table_county$o_rourke)
table_county$dikeman <- gsub(",","",table_county$dikeman)

table_county = 
  table_county %>% 
  mutate(cruz = as.numeric(cruz), o_rourke = as.numeric(o_rourke), dikeman = as.numeric(dikeman))

table_county$county = str_replace(table_county$county,"La Vaca", "Lavaca")
table_county$county = str_replace(table_county$county,"De Witt", "DeWitt")
#county names misspelled (was causing issues with merging later on)
table_county_long = gather(table_county, key = candidate, value = votes, cruz:dikeman)
```


Made the second table which has all of the 254 county level data for Texas!

## Plots for all counties


```{r}
point_county =
  table_county %>% 
  select(-"dikeman") %>%
  mutate(total = cruz + o_rourke) %>% 
  arrange(desc(total)) %>% 
  top_n(5) %>% 
  gather(key = candidate, value = votes, cruz:o_rourke) %>% 
  ggplot(aes(x = county, y = votes, color = candidate)) +
  geom_point() +
  labs(
    title = "Number of Votes for Beto vs Cruz",
    x = "County",
    y = "Number of Votes"
  ) +
  theme(axis.text.x = element_text(angle = 90))
  
point_county
```




## comparing these county level election results to highly searched voter election interests in google
-using search terms "Midterms" and selecting dataset from top result

```{r reading in dataset voter searches}

district_searches = read_csv(file =  "./data/Search_Data_US_Congressional_District_26Sep2018.csv")

```


```{r Tx subdata}

TX_searches = 
  district_searches %>% janitor::clean_names() %>% 
  filter(state == "TX")

TX_counts = 
  TX_searches %>% 
  count(fifth)


#the topics that were searched most were health care, immigration, mental health, united nations
#second most searched: immigration, health care, Medicare, Medicaid, capital punishment
#third most searched: Medicare, Medicaid, September 11 attacks, immigration, 
#fourth most searched: Medicaid, Medicare, Immigration...
#fifth: Medicaid, mental health, Medicare, September 11 attacks...
#Thus, we should focus on the variables health care, immigration, Medicare, Medicaid, Mental health, September 11 attacks
```

##uploading county congressional district txt file

```{r 113th congressional district table}

congress_district = read.csv(file = "./data/congress_district2.csv") 

congress_district$county_name = str_replace(congress_district$county_name,"Sterlin", "Sterling")
congress_district$county_name = str_replace(congress_district$county_name,"MuCulloch","McCulloch")
#misspelled counties discovered while exploring data when merging later on
```

```{r merge searches with congress district dataset}
TX_searches =
  TX_searches %>% 
  separate(code, into = c("remove_1", "district_num"), sep = "-") %>% 
  mutate(district_num = as.numeric(district_num)) %>% 
  select(district_num, most_searched = first, x2003_invasion_of_iraq:womens_health) 

nested_congress =
  congress_district %>% 
  nest(county_name) 
	
merged_searches= merge(TX_searches, nested_congress, by="district_num", all=TRUE) %>% 
  unnest() 

#rename variable county_name
merged_searches = merged_searches %>% 
  select(district_num, county=county_name, everything())

merged_nyt_searches = merge(merged_searches, table_county, by= "county", all=TRUE)

```

#plot for topics search per county
Still figuring out how to display this
ideas: 1) interactive barchart in the current long format, if we use shiny we could show how the top topics vary among counties through use of drop-down menu to select county, etc.
2) figure out we can juxtapose how the counties voted vs. topics. Use of plotly for interactivity?
3) Alternative to first option, how can we show the distribution of topics among counties instead?
4)focus on 5 biggest counties or districts? but this would be biased as it may be a metropolitan area
```{r long format merged}
merged_nyt_searches_long = gather(merged_nyt_searches, key = topics, value = search_interest, health_care:september_11_attacks)

```



## comparing these county level election results to search results by candidate

## map
```{r cleaning data for use with map}
merged_nyt_searches = read_csv(file ="./data/merged_nyt_searches.csv") #previously merged_nyt_searches dataframe into a csv file

gis = merged_nyt_searches %>% 
  select(county, most_searched, cruz, o_rourke, dikeman) %>% 
  mutate(cruz_orour_rat = cruz/o_rourke,
         status = as.numeric(cruz_orour_rat>=1),
         winner = ifelse(status==1, "Ted Cruz", "Beto O'Rourke"))

gis = unique(gis) 

gis = gis %>% 
nest(most_searched) 

listcollapse = function(x){
  paste(unlist(x), collapse = ", ")
}

gis = gis %>% 
  mutate( most_searched = map(data, listcollapse)) %>% 
  select(-data)

```

Cleaning data so as to merge with GIS...
```{r GIS file merge}
texas_counties = counties(state = "48",year = "2017") #Texas fips code is 48, using most recent census data, 2017

tx_midterms = geo_join(texas_counties, gis, "NAME", "county")
```

```{r specifying what goes into map}
pal = colorFactor(c("blue", "red"), tx_midterms$status)

popup = paste(sep = "<br/>",
              paste0("<b>Winner: </b>", tx_midterms$winner),
              paste0("<b>County: </b>", tx_midterms$county),
              paste0("<b>Votes for Ted Cruz: </b>", tx_midterms$cruz),
              paste0("<b>Votes for Beto O'Rourke: </b>", tx_midterms$o_rourke),
              paste0("<b>Votes for Neal Dikeman: </b>", tx_midterms$dikeman),
              paste0("<b>Most searched topics over one month prior: </b>", tx_midterms$most_searched))
```

```{r making the map using leaflet}
leaflet(tx_midterms) %>% 
  addProviderTiles("CartoDB.Positron") %>% 
  addPolygons(fillColor= ~pal(status),
              color = "black",
              popup = popup,
              fillOpacity = 0.5,
              weight = 0.5) %>% 
  addLegend(position = "bottomleft",
            colors = c("blue", "red"),
            labels = c("Democrat", "Republican"),
            opacity = 1,
            title = "2018 Texas Senate Election Results")
```

