---
title: "most_searched_topics"
author: "Helen"
date: "11/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
district_searches2 = read_csv(file =  "./data/Search_Data_US_Congressional_District_26Sep2018.csv")
```

# Using Search Data US Congressional District Sep 26 Dataset 

```{r}
# Limit tx_searches dataset to only Texas rows and all the topic columns
tx_searches = 
  district_searches2 %>% janitor::clean_names() %>% 
  filter(state == "TX") %>% 
  select(district, x2003_invasion_of_iraq:womens_health)
```

```{r}
# Summing up the relative searched frequencies of each topic to get the 5 most searched topics in Texas 
tx_searches_sum = colSums(tx_searches[,-1])

# According to the searched frequencies, the five most searched topics are:
# * health_care 509.87
# 
# * immigration 357.52
# 
# * medicare 270.02
# 
# * medicaid 234.14
# 
# * september_11_attacks 195.37 
```



### Looking at the top 4 most populated districts in Texas
According to https://www.census.gov/mycd/, the top most populated districts in Texas are: Districts 22, 26, 3, 8, 31 

```{r}
tx_searches_population = 
  tx_searches %>% 
  filter(district %in% c("Texas 22nd", "Texas 26th", "Texas 3rd", "Texas 8th", "Texas 31st")) %>%
  select(district, health_care, immigration, medicare, medicaid, september_11_attacks) %>% 
  gather(key = topics, value = searched_freq, health_care:september_11_attacks) 
```


```{r}
# Stacked bar graph
# tx_searches_population %>% 
#   ggplot(aes(x = district, y = searched_freq)) +
#   geom_bar(aes(fill = topics), stat = "identity") 
```


```{r}
# Multiple bars bar graph
tx_searches_population %>%
  ggplot(aes(district, searched_freq)) +   
  geom_bar(aes(fill = topics), position = "dodge", stat = "identity")
```


```{r}
# Facet by the districts
# (I don't know why the bars won't change color...)
# tx_searches_population %>%
#   ggplot(aes(x = topics, y = searched_freq)) +   
#   geom_bar(aes(color = topics), position = "dodge", stat = "identity") +
#   facet_wrap(~district)
```

### Looking at the most Democrats vs Republicans districts in Texas

Using the Cook Partisan Voting Index (PVI) as a measure (https://www.cookpolitical.com/index.php/pvi-map-and-district-list), 

* the most Democrats districts are: 9, 30, 18, 33
* the most Republicans districts are: 13, 11, 8, 4

Created a "party" varible to identify the Democrats and Republicans districts
```{r}
tx_searches_pvi = 
  tx_searches %>% 
  filter(district %in% c("Texas 9th", "Texas 30th", "Texas 18th", "Texas 33rd", "Texas 13th", "Texas 11th", "Texas 8th", "Texas 4th")) %>%
  select(district, health_care, immigration, medicare, medicaid, september_11_attacks) %>% 
  gather(key = topics, value = searched_freq, health_care:september_11_attacks) %>% 
  mutate(party = ifelse(district %in% c("Texas 9th", "Texas 30th", "Texas 18th", "Texas 33rd"), "Democrats", "Republicans"))
```


```{r}
# Stacked bar graph
# tx_searches_pvi %>% 
#   ggplot(aes(x = district, y = searched_freq)) +
#   geom_bar(aes(fill = topics), stat = "identity") 
```

```{r}
# Multiple bars bar graph
tx_searches_pvi %>%
  ggplot(aes(district, searched_freq)) +   
  geom_bar(aes(fill = topics), position = "dodge", stat = "identity")
```


```{r}
# Facet by the districts
# (I don't know why the bars won't change color...)
tx_searches_pvi %>%
   ggplot(aes(x = topics, y = searched_freq)) +   
   geom_bar(aes(color = topics), position = "dodge", stat = "identity") +
   facet_wrap(~district)
```

#### Recreate same graphs using party variable 


```{r}
# Stacked bar graph
# tx_searches_pvi %>% 
#   ggplot(aes(x = party, y = searched_freq)) +
#   geom_bar(aes(fill = topics), stat = "identity") 
```


```{r}
# Multiple bars bar graph
tx_searches_pvi %>%
  ggplot(aes(party, searched_freq)) +   
  geom_bar(aes(fill = topics), position = "dodge", stat = "identity")
```


```{r}
# Facet by the party
tx_searches_pvi %>%
  ggplot(aes(x = topics, y = searched_freq)) +   
  geom_bar(position = "dodge", stat = "identity") +
  facet_wrap(~party)
```

### Looking at the top searched topics across all districts 
```{r}
tx_all = 
  tx_searches %>% 
  select(district, health_care, immigration, medicare, medicaid, september_11_attacks) %>% 
  gather(key = topics, value = searched_freq, health_care:september_11_attacks) 
```


```{r}
# Stacked bar graph
# tx_all %>% 
#   ggplot(aes(x = district, y = searched_freq)) +
#   geom_bar(aes(fill = topics), stat = "identity") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
# Facet across districts showing all five searched topics 
# tx_all %>%
#   ggplot(aes(topics, searched_freq)) +   
#   geom_bar(aes(fill = topics), position = "dodge", stat = "identity") +
#   facet_wrap(~district) +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r}
# Healthcare across all districts
# tx_all %>%
#   filter(topics == "health_care") %>%
#   ggplot(aes(x = district, y = searched_freq)) +   
#   geom_bar(position = "dodge", stat = "identity") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r}
# Same graph by sort by searched_freq
# tx_all %>%
#   filter(topics == "health_care") %>%
#   mutate(district = fct_reorder(district, searched_freq)) %>% 
#   ggplot(aes(x = district, y = searched_freq)) +   
#   geom_bar(position = "dodge", stat = "identity") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
# Immigration across all districts 
# tx_all %>%
#   filter(topics == "immigration") %>%
#   ggplot(aes(x = district, y = searched_freq)) +   
#   geom_bar(position = "dodge", stat = "identity") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
# Same graph but sort by searched_freq
# tx_all %>%
#   filter(topics == "immigration") %>%
#   mutate(district = fct_reorder(district, searched_freq)) %>% 
#   ggplot(aes(x = district, y = searched_freq)) +   
#   geom_bar(position = "dodge", stat = "identity") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

