---
title: "statistical testing"
author: "Courtney Chan"
date: "December 3, 2018"
output: github_document
---

#Trying linear regression with dataset merged_nyt_searches

##First creating the dataset


```{r packages, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(ggridges)
library(tigris)
library(leaflet)
library(dplyr)
library(purrr)


```

##scraping election results from the web

###New York Times voting results by county

```{r scraping election results for texas from the web table method, include=FALSE}

url = "https://www.nytimes.com/elections/results/texas-senate"
nytimes_data = read_html(url, col_types = "ccdd")

nytimes_data

```

```{r extracting tables from website, include=FALSE}
nytimes_data %>% 
  html_nodes(css = "table")

```
This seems to have created two tables from the website data.

```{r making 1st web table into tibbles, include=FALSE}

table_overall = (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[1]] %>%
  html_table()
```

## Tidying overall table for exploratory analysis

```{r tidy overall, include=FALSE}
#remove the commas in the numbers first
table_overall$Votes <- gsub(",","",table_overall$Votes)
table_overall$Pct. <- gsub("%","",table_overall$Pct.)

#convert votes and percent to numeric
table_overall = 
  table_overall %>% 
  mutate(Votes = as.numeric(Votes), Pct. = as.numeric(Pct.))
```

## Bar Plot of Votes per Candidate

```{r bar_plot, echo=FALSE}
bar_overall =
  table_overall %>% 
  mutate(Candidate = as.factor(Candidate)) %>% 
  mutate(Candidate = forcats::fct_reorder(Candidate, Votes)) %>% 
  ggplot(aes(x = Candidate, y = Votes, fill = Party)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Number of Votes per Candidate",
    x = "Candidate",
    y = "Number of Votes"
  ) +
  scale_x_discrete(labels = c("Cruz* Ted Cruz*" = "Ted Cruz", "O'Rourke Beto O'Rourke" = "Beto O'Rourke",
                              "Dikeman Neal Dikeman" = "Neal Dikeman"))
  
bar_overall
```

This plot illustrates how it was a close race between the top two candidates, O'Rourke and Cruz. As Dikeman had very few votes, we decided to omit Dikeman from further analyses.

Made the first table that which we have final results for the state of texas.

```{r making 2nd web table into another tibble, include=FALSE}

table_county =  (nytimes_data %>% html_nodes(css = "table")) %>% 
  .[[2]] %>%
  html_table() %>% 
  slice(1:(n() - 1)) %>% 
  select(-Rpt.) %>% 
  janitor::clean_names()

```

## Tidying county table

```{r tidy county, include=FALSE}
#remove the commas in the numbers first
table_county$cruz <- gsub(",","",table_county$cruz)
table_county$o_rourke <- gsub(",","",table_county$o_rourke)
table_county$dikeman <- gsub(",","",table_county$dikeman)

table_county = 
  table_county %>% 
  mutate(cruz = as.numeric(cruz), o_rourke = as.numeric(o_rourke), dikeman = as.numeric(dikeman))

table_county$county = str_replace(table_county$county,"La Vaca", "Lavaca")
table_county$county = str_replace(table_county$county,"De Witt", "DeWitt")
#county names misspelled (was causing issues with merging later on)
table_county_long = gather(table_county, key = candidate, value = votes, cruz:dikeman)
```


Made the second table which has all of the 254 county level data for Texas!

## Plots for all counties

```{r point county, echo=FALSE, message=FALSE}
  table_county %>% 
  select(-"dikeman") %>%
  mutate(total = cruz + o_rourke) %>% 
  arrange(desc(total)) %>% 
  top_n(5) %>% 
  gather(key = candidate, value = votes, cruz:o_rourke) %>% 
  ggplot(aes(x = county, y = votes, color = candidate)) +
  geom_point() +
  labs(
    title = "Number of Votes for Beto vs Cruz",
    x = "County",
    y = "Number of Votes"
  ) +
  theme(axis.text.x = element_text(angle = 90))

```




## comparing these county level election results to highly searched voter election interests in google
-using search terms "Midterms" and selecting dataset from top result

```{r reading in dataset voter searches, include=FALSE}

district_searches = read_csv(file =  "./data/Search_Data_US_Congressional_District_26Sep2018.csv")

```


```{r Tx subdata, include=FALSE}

TX_searches = 
  district_searches %>% janitor::clean_names() %>% 
  filter(state == "TX")

TX_counts = 
  TX_searches %>% 
  count(fifth)


#the topics that were searched most were health care, immigration, mental health, united nations
#second most searched: immigration, health care, Medicare, Medicaid, capital punishment
#third most searched: Medicare, Medicaid, September 11 attacks, immigration, 
#fourth most searched: Medicaid, Medicare, Immigration...
#fifth: Medicaid, mental health, Medicare, September 11 attacks...
#Thus, we should focus on the variables health care, immigration, Medicare, Medicaid, Mental health, September 11 attacks
```

##uploading county congressional district txt file

```{r 113th congressional district table, include=FALSE}

congress_district = read.csv(file = "./data/congress_district2.csv") 

congress_district$county_name = str_replace(congress_district$county_name,"Sterlin", "Sterling")
congress_district$county_name = str_replace(congress_district$county_name,"MuCulloch","McCulloch")
#misspelled counties discovered while exploring data when merging later on
```

```{r merge searches with congress district dataset, include=FALSE}
TX_searches =
  TX_searches %>% 
  separate(code, into = c("remove_1", "district_num"), sep = "-") %>% 
  mutate(district_num = as.numeric(district_num)) %>% 
  select(district_num, most_searched = first, x2003_invasion_of_iraq:womens_health) 

nested_congress =
  congress_district %>% 
  nest(county_name) 
	
merged_searches= merge(TX_searches, nested_congress, by="district_num", all=TRUE) %>% 
  unnest() 

#rename variable county_name
merged_searches = merged_searches %>% 
  select(district_num, county=county_name, everything())

merged_nyt_searches = merge(merged_searches, table_county, by= "county", all=TRUE)

```

#plot for topics search per county
Still figuring out how to display this
ideas: 1) interactive barchart in the current long format, if we use shiny we could show how the top topics vary among counties through use of drop-down menu to select county, etc.
2) figure out we can juxtapose how the counties voted vs. topics. Use of plotly for interactivity?
3) Alternative to first option, how can we show the distribution of topics among counties instead?
4)focus on 5 biggest counties or districts? but this would be biased as it may be a metropolitan area
```{r long format merged, include=FALSE}
merged_nyt_searches_long = gather(merged_nyt_searches, key = topics, value = search_interest, health_care:september_11_attacks)

```

```{r visually assessing counts}

merged_nyt_searches %>% 
  gather(key = candidate, value = vote_count, cruz:dikeman) %>% 
  ggplot(aes(x = vote_count, fill = candidate)) + geom_histogram(position = "dodge")

```

```{r lm health care vs. votes}

health_most_searched = merged_nyt_searches %>% 
  mutate(most_searched = recode(most_searched, "Health care" = "Health care", .default = "Not Health care")) %>% 
  mutate(most_searched = factor(most_searched, levels = c("Not Health care", "Health care")))

lm_healthcare_o = lm(o_rourke ~ most_searched, data = health_most_searched) %>% broom::tidy()

lm_healthcare_cruz = lm(cruz ~ most_searched, data = health_most_searched) %>% broom::tidy()

lm_healthcare_dikeman = lm(cruz ~ most_searched, data = health_most_searched) %>% broom::tidy()

```

```{r lm most_searched vs. votes}

unique(merged_nyt_searches_long$most_searched)

df_most_searched = merged_nyt_searches %>% 
  mutate(most_searched = factor(most_searched, levels = c("Immigration", "United Nations", "Mental health", "Health care")))

lm_most_searched_o = lm(o_rourke ~ most_searched, data = df_most_searched) %>% broom::tidy()

lm_most_searched_cruz = lm(cruz ~ most_searched, data = df_most_searched) %>% broom::tidy()

lm_most_searched_dikeman = lm(dikeman ~ most_searched, data = df_most_searched) %>% broom::tidy()

```

```{r logistic}
merged_nyt_searches %>% 
  mutate()

```